### 2017-06-28 Kokkos_PG_HierarchicalParallelism.tex
Reformat lines overrunning margins

The total amount of scratch space available for each team will be the per-team value plus the per-thread value multiplied by the team-size. 
The interface allows users to specify those settings inline:
\begin{lstlisting}
parallel_for(TeamPolicy<>(league_size, team_size).set_scratch_size(1, PerTeam(1024)),
  KOKKOS_LAMBDA (const TeamPolicy<>::member_type& team) {
    ...
});
\end{lstlisting}

>>>>

The total amount of scratch space available for each team will be the per-team value plus the per-thread value multiplied by the team-size. 
The interface allows users to specify those settings inline:
\begin{lstlisting}
parallel_for(
  TeamPolicy<>(league_size, team_size).set_scratch_size(1, PerTeam(1024)),
    KOKKOS_LAMBDA (const TeamPolicy<>::member_type& team) {
    ...
});
\end{lstlisting}
